HO unification from object language to meta language

### 2024-03-20 paper/appendix.tex
appendix: update progress

>>>>

  type same-link-eta link -> link -> ho.subst -> ho.subst -> o.
  same-link-eta (ho.abs F) B H H1 :- !, pi x\ same-link-eta (F x) B H H1.
  same-link-eta A (ho.abs G) H H1 :- !, pi x\ same-link-eta A (G x) H H1.
  same-link-eta (@val-link-eta (ho.uva N S1) A)
                (@val-link-eta (ho.uva N S2) B) H H1 :-
    std.map2 S1 S2 (x\y\r\ r = ho.copy x y) Perm,
    Perm => ho.copy A A',
    (A' ==l B) H H1.
